Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2019-11-04 paper/paper.tex
notebook figure addded
added nbtranslate

Generally speaking, a Jupyter notebook is a document mixing prose,
code, visualization, together with resources: source code, data,
media.  It consists of a collection of two types of cells, namely code
cells and text cells. The latter may contain text written in markdown,
possibly including formulas as well as figures. This structure
facilitates to guide students through a problem set.

Jupyterhub as a centrally provided resource to run a Jupyter notebook from a
remote computer makes problem sets or more generally teaching material easily
accessible without the need for a local Python installation. Furthermore, this
approach ensures a consistent working environment for all students. However,
it might be an important experience for students that all work which they
are doing could in fact be done on their own computer instead of using some
remote service where the underlying machinery is completely hidden.

@@

>>>>

Generally speaking, a Jupyter notebook is a document mixing prose,
code, visualization, together with resources: source code, data,
media.  It consists of a collection of two types of cells, namely code
cells and text cells (see fig. \ref{fig:notebook}). The latter may
contain text written in markdown, possibly including formulas as well
as figures. This structure facilitates to guide students through a
problem set.

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figs/notebook.png}
\caption{Jupyter notebooks is a executable document which contains
  rich-text and code (e.g. in Pyton). }
\label{fig:notebook}
\end{figure}

Jupyter notebook has recenely been popular among researchers as it can
embody the FAIR (Findable, Accessible, Interoperable, Reusable)
principles for scholarly communication \cite{Randles2017}. The number
of notebooks which are publically available on github now exceeds 5
milion.

Jupyterhub a software providing a way to serve Jupyter notebook for
multiple users. It can be used in a classes of students, all

 a centrally provided resource to run a Jupyter notebook from a
remote computer makes problem sets or more generally teaching material easily
accessible without the need for a local Python installation. Furthermore, this
approach ensures a consistent working environment for all students. However,
it might be an important experience for students that all work which they
are doing could in fact be done on their own computer instead of using some
remote service where the underlying machinery is completely hidden.

@@

\bibitem{Randles2017}
B. M. {Randles} and I. V. {Pasquetto} and M. S. {Golshan} and C. L. {Borgman}
2017 ACM/IEEE Joint Conference on Digital Libraries (JCDL),
2017, doi={10.1109/JCDL.2017.7991618}
